---
title: 'Launchpad'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load packages for data analysis
# install.packages("gsheet")
# install.packages("tidyverse")
# install.packages("kableExtra")
library(gsheet)
library(tidyverse)
library(kableExtra)
options(digits = 3)
options(scipen = 999)
```

# SwapScore vs DASH vs HybridScore

The script gets `DASH`, `SwapScore` and wallet `Address` from the googlesheet. It adds colums:
    + `Srank`: SwapScore ranking (wallet `Address` is sorted by this variable).
    + `Swins`: The expected winning tickets one would receive if the total number of   launchpad slots in a NFT system based on `SwapScore` would be 1000 (one launchpad slot = one winning ticket).
    + `cSwins`: The cumulative sum of `Swins`.
    + `Drank`: DASH ranking.
    + `Dwins`: The right to participate in the launchpad (coded as 1, otherwise 0) if you are one of the top 1000 DASH holders (equivalent to receiving one winning ticket in a NFT system). 
    + `HybridScore`: A hybrid score computed as `SwapScore * DASH`.
    + `Hrank`: HybridScore ranking.
    + `Hwins`: The expected winning tickets one would receive if the total number of   launchpad slots in a NFT system based on `SwapScore * DASH` would be 1000 (one launchpad slot = one winning ticket).
    + `cHwins`: The cumulative sum of `Hwins`.


```{r message=FALSE, warning=FALSE}
# Get DASH data from google sheet
DASH_url <- "https://docs.google.com/spreadsheets/d/1omcvXGOg9NhN-MxiyIhacsq8u8Vw4Wou8Q8CsJ1pXho/edit#gid=513362759"
DASH_data <- gsheet2tbl(DASH_url)

# Get SwapScore data from google sheet
SwapScore_url <- "https://docs.google.com/spreadsheets/d/1omcvXGOg9NhN-MxiyIhacsq8u8Vw4Wou8Q8CsJ1pXho/edit#gid=1846578663"
SwapScore_data <- gsheet2tbl(SwapScore_url)

# Join SwapScore and Dash data
# Arrange row form high to low SwapScore
# Add ranking columns
# Add (expected) wins if launchpad slots = 1000
# Add cumulative wins for SwapScore = cumSwapScore_wins
slots = 1000
data <-
  SwapScore_data %>% 
  inner_join(DASH_data, by = "Address") %>% 
  mutate(HybridScore = SwapScore * DASH) %>% 
  arrange(-SwapScore) %>% 
  mutate(Srank = rank(-SwapScore),
         Drank = rank(-DASH),
         Hrank = rank(-HybridScore)) %>% 
  mutate(Swins = as.numeric(SwapScore / sum(SwapScore) * slots),
         Dwins = as.numeric(Drank <= slots),
         Hwins = as.numeric(HybridScore / sum(HybridScore) * slots)) %>% 
  mutate(cSwins =cumsum(Swins),
         cDwins =cumsum(Dwins),
         cHwins =cumsum(Hwins))

# Show data in a table
data %>% 
  select(Address, 
         SwapScore,
         Srank,
         Swins,
         cSwins,
         DASH,
         Drank, 
         Dwins,
         cDwins,
         HybridScore,
         Hrank,
         Hwins,
         cHwins,) %>% 
  kable("html") %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```
