---
title: 'Launchpad'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load packages for data analysis
# install.packages("gsheet")
# install.packages("tidyverse")
# install.packages("kableExtra")
library(gsheet)
library(tidyverse)
library(kableExtra)
options(digits = 3)
options(scipen = 999)
```

# Description of method

The script pulls `DASH`, `SwapScore` and wallet `Address` from the googlesheet provided by the Trustswap team. It computes the number of wallets `n` with a DASH of at least 2000 -- the presale criterion for Mobiepay and Aubit -- and adds the following columns to the data table:

  + `Srank`: SwapScore ranking (wallet `Address` is sorted by this variable).
  + `Swins`: The expected tickets for the wallet that selected in the allocation mining procedure = winning tickets. Assumptions: Allocation mining procedure used in the selection of the Aubit golden tickets, number of tickets selected is `n`, each wallet receives entry tickets equal to `SwapScore` and all entry tickets are used in the presale.
  + `cSwins`: The cumulative sum of `Swins`.
  
  + `Drank`: DASH ranking.
  + `Dwins`: Access to participate in the presale coded as 1, otherwise 0. The number is comparable to the expected number of selected entry tickets by the allocation mining procedure.
  
  + `HybridScore`: A hybrid score computed as `SwapScore * DASH` proposed by the Trustswap community members.
  + `Hrank`: HybridScore ranking.
  + `Hwins`: The expected winning tickets. Same assumptions as `Swins` but number of entry tickets of wallet = `HybridScore`.
  + `cHwins`: The cumulative sum of `Hwins`.
  
# Code

```{r message=FALSE, warning=FALSE}
# Get DASH data from google sheet
DASH_url <- "https://docs.google.com/spreadsheets/d/1omcvXGOg9NhN-MxiyIhacsq8u8Vw4Wou8Q8CsJ1pXho/edit#gid=513362759"
DASH_data <- gsheet2tbl(DASH_url)

# Get SwapScore data from google sheet
SwapScore_url <- "https://docs.google.com/spreadsheets/d/1omcvXGOg9NhN-MxiyIhacsq8u8Vw4Wou8Q8CsJ1pXho/edit#gid=1846578663"
SwapScore_data <- gsheet2tbl(SwapScore_url)

# number of with a DASH equal or greater than 2000 
n = sum(DASH_data$DASH >= 2000)

# Join SwapScore and Dash data
# Arrange row form high to low SwapScore
# Add ranking columns
# Add (expected) wins if launchpad slots = 1000
# Add cumulative wins for SwapScore = cumSwapScore_wins

slots = n
data <-
  SwapScore_data %>% 
  inner_join(DASH_data, by = "Address") %>% 
  mutate(HybridScore = SwapScore * DASH) %>% 
  arrange(-SwapScore) %>% 
  mutate(Srank = rank(-SwapScore),
         Drank = rank(-DASH),
         Hrank = rank(-HybridScore)) %>% 
  mutate(Swins = as.numeric(SwapScore / sum(SwapScore) * slots),
         Dwins = as.numeric(Drank <= slots),
         Hwins = as.numeric(HybridScore / sum(HybridScore) * slots)) %>% 
  mutate(cSwins =cumsum(Swins),
         cDwins =cumsum(Dwins),
         cHwins =cumsum(Hwins))
```

# Comparison of results for selected wallets

```{r}
cat("Number of people with a DASH of at least 2000: ", n)
```

```{r}
SwapScoreRank <- c(1, 10, 25, 50, 100, 150, 200, 250, 375, 500, 750, 1000, 1250, 1500, 1750, 2000, 2250, 2500)
  
# Show data in a table with scroll functionality
data %>% 
  slice(SwapScoreRank) %>% 
  select(Address, 
         SwapScore,
         Srank,
         Swins,
         cSwins,
         DASH,
         Drank, 
         Dwins,
         cDwins,
         HybridScore,
         Hrank,
         Hwins,
         cHwins,) %>% 
  kable("html") %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```


# Results for all wallets

```{r}
# Show full data in a table with scroll functionality
data %>% 
  select(Address, 
         SwapScore,
         Srank,
         Swins,
         cSwins,
         DASH,
         Drank, 
         Dwins,
         cDwins,
         HybridScore,
         Hrank,
         Hwins,
         cHwins,) %>% 
  kable("html") %>% 
  kable_styling("striped") %>% 
  scroll_box(width = "100%")
```